Summary of tumor cell classification with `AUCell` for `r params$library_id`

### 2024-07-12 analyses/cell-type-ewings/template_notebooks/auc-workflow/01-auc-results.Rmd
export marker gene classification

---
title: "Summary of tumor cell classification with `AUCell` for `r params$library_id`"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  library_id: NULL
  sce_file: NULL
  aucell_results_file: NULL
  ref_auc_results: NULL
  geneset_scores_file: NULL
  marker_genes_file: NULL
  auc_threshold: NULL
---

This report summarizes the classification of `r params$library_id` using [`AUCell`](https://www.bioconductor.org/packages/release/bioc/html/AUCell.html). 
Cells were classified as tumor if they had an AUC value greater than or equal to `r params$auc_threshold`.

@@

>>>>

---
title: "Summary of tumor cell classification with `AUCell` for `r params$library_id`"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: "hide"
params:
  library_id: NULL
  sce_file: NULL
  aucell_results_file: NULL
  ref_auc_results: NULL
  geneset_scores_file: NULL
  marker_genes_file: NULL
  output_file: NULL
  auc_threshold: NULL
---

This report summarizes the classification of `r params$library_id` using two methods:

- [`AUCell`](https://www.bioconductor.org/packages/release/bioc/html/AUCell.html): Cells are classified as tumor if they had an AUC value greater than or equal to `r params$auc_threshold`. 
- Marker gene expression: Cells were classified as tumor if they expressed any tumor marker genes.

@@

## Save marker gene classification

```{r}
classification_df |> 
  dplyr::filter(method == "marker_gene_classification") |> 
  dplyr::select(barcodes, marker_gene_classification = classification) |> 
  readr::write_tsv(params$output_file)
```
